Effects of epidemiological structure on the transient evolution of HIV virulence

### 2016-12-13 ms/cover_letter/plosHIVcover_resubm2.tex
cover letter updates for abstract & author summary

%\response{}

@@

>>>>

\response{We have modified the first few sentences to make them
more concrete and (hopefully) more understandable. 
Yes, we did mean that the stage of the epidemic is a strong
driver of virulence evolution, and the one we focus on here.
We have removed the potentially confusing term ``fitness landscape''.

The point about initial virulence being measured immediately after
a species jump is interesting, but since it is somewhat peripheral
to our main exploration here, we have opted to include in the 
Discussion rather than trying to squeeze it into the abstract
\textbf{don't forget to do this}
}

@@

\response{We were previously trying to pack too many ideas into a few sentences. We have made the text more concrete, clarifying that we do indeed mean to describe the fact that prevalence changes over the course of the epidemic, and that this changes the evolutionary environment for the pathogen.}
